%Acknowledgements
\chapter*{\centering \Large \vspace{-20mm}\Huge Acknowledgements}

Firstly, I would like to thank my supervisors Dr. Tristan Quaife, Dr. Sarah Dance, Dr. Amos Lawless, Dr. James Morison and Prof. Nancy Nichols for their excellent support, guidance and encouragement throughout my PhD project, this is also true for Dr. Eric Casella and Matt Wilkinson who were not supervisors but were heavily involved with the PhD. Their input from a variety of backgrounds has helped improve my understanding and see problems from alternative perspectives. I would also like to thank Ed Eaton along with others from Forest Research for all the help they gave during my fieldwork at the Alice Holt forest and useful input during the PhD. I appreciate the input of my monitoring committee members Dr. Jochen Broecker and Dr. Nicolas Bellouin for keeping me on track and helping me see the progress I had made every 6 months. I also acknowledge the financial support of the National Environmental Research Council (NERC) without which this project would not be possible.

I would like to extend my thanks to all my colleagues who make the department such an enjoyable place to be and helped to lighten the mood with activities such as the pantomime. Finally I would like to thank my friends and family for their continued support and understanding. Thanks to my parents and in particular my Dad who has always been the smartest person I know, also my partner Maria who has given up many of her weekends to help me take observations and spray paint trees at the Alice Holt forest.  

   

\vspace{2cm}

\newpage
